---
title: "Week10 Day01 Homework"
output: html_notebook
---


```{r}
library(tidyverse)
library(janitor)
library(broom)
library(modelr)
```

```{r}
raw_proj_mang <- read_csv("data/project_management.csv") %>% 
  clean_names()
```
independent = x =est_len
dependent = y = act_len

# Correlation Coefficient

Estimated_length and actual length generates a correlation coefficient of 0.805...meaning it has a very strong strength of correlation.
Plot shows evidence that the estimated_length and actual_length has a linear relationship that is suitable for correlation analysis.
It has a trend with random spread of the data points, where as est_len, the act_len also increases, with an exception of an outlier at est_len ~ 20.0


```{r}
# Plot Est_len vs Act_len
plot_proj_mang <- raw_proj_mang %>% 
  ggplot()+
  aes(x = estimated_length, y = actual_length)+
  geom_point()

# Correlation coefficient
correlation_coefficient <- raw_proj_mang %>% 
  summarise(cor_coe = cor(actual_length, estimated_length))


plot_proj_mang
correlation_coefficient
```

```{r}
model <- lm(formula = actual_length ~ estimated_length, data = raw_proj_mang)
summary(model)
```
```{r}
glance_output <- clean_names(glance(model))
glance_output$r_squared

```

```{r}

```







