---
title: "wk06_day05_hw"
output:
  html_document:
    df_print: paged
---
```{r}
library(tidyverse)
library(janitor)
library(infer)

```

## Task 01 - Question 02

```{r}
data(msleep) %>% 
  summarise(mean_sleep_total = mean(as.numeric(sleep_total)))
```

## Task 02 - Question 1
Test Type:  One Sample Proportion...
Method Type: "Draw" or "Permute"
Direction: "Less"
Setup for Hypothesis Test:
$$H_{0}:\mu_{popularity} < 0.4$$
$$H_{a}: \Delta\mu \geq 0.4$$


## Task 02 - Question 2
Test Type:  Two Samples Pairing Proportion...
Method Type: permute
Setup for Hypothesis Test:
Direction: "Both"
$$H_{0}:\mu_{A_prop} - \mu_{B_prop} = 0$$
$$H_{a}: \Delta\mu \neq 0$$
## Task 02 - Question 3
Test Type:  One Sample Mean...
Method Type: bootstrap
Direction: "Both"
Setup for Hypothesis Test:
$$H_{0}:\mu_{part width} = 145$$
$$H_{a}: \mu_{part width} \neq 145$$


## Task 03 - Question 1
CI = 0.05 (5%)
p-value = 0.07(7%)
$$H_{0} = TRUE$$, Accept `H_{0}` as the P value is within the 5% CI, that 40% of the population know the coffee shop.

## Task 03 - Question 2
CI = 0.01 (1%)
p-value = 0.006(0.6%)
$$H_{0} = FALSE$$, Reject `H_{0}` as the P value is outwith the 1% CI.

## Task 03 - Question 3
CI = 0.05 (5%)
p-value = 0.55(55%)
$$H_{0} = TRUE$$, Accept `H_{0}`, as the p value is within the 5% CI, the process is indeed difted from its original dimension as the part is significaly away from 145mm.