---
title: "Week11 Day03 Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(cluster)
library(factoextra)
library(dendextend)
library(corrplot)
library(janitor)
library(broom)
```

```{r}
cust_raw <- read_csv("data/mall_customers.csv")
```

```{r}
#sanity check for NA
any(is.na(cust_raw))
```

```{r}
cust <- cust_raw %>% 
  clean_names() %>% 
  rename(score = spending_score_1_100,
         income = annual_income_k) %>% # Rename col-names for simplicity
  select(-gender, -customer_id, -age) # Drop cat-variable, gender for simplicity 
```

```{r}
# cust %>% 
#   group_by(gender) %>% 
#   summarise(income_mean = round(mean(income)),
#             income_sd = sd(income),
#             score_mean = round(mean(score)),
#             score_sd = sd(score))
# 
# GGally::ggpairs(cust)
```
```{r}
cust_scale <- cust %>% 
  mutate_all(scale)

cluster_cust <- kmeans(cust_scale,
                       centers = 2,
                       nstart = 25)
cluster_cust
```

```{r}
tidy(cluster_cust,
     col.names = colnames(cust_scale))

augment(cluster_cust, cust)
glance(cluster_cust)
```

```{r}
max_k <- 20
k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(cust_scale, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, cust)
  )

k_clusters
```


```{r}
clusterings <- k_clusters %>% 
  unnest(glanced)

# Elbow Plot
fviz_nbclust(cust_scale, 
             kmeans, 
             method = "wss", 
             nstart = 25)+
  labs(title = "Elbow Diagram")

# Silhouette coefficient
fviz_nbclust(cust_scale, 
             kmeans, 
             method = "silhouette", 
             nstart = 25)+
  labs(title = "Silhouette Diagram")

fviz_nbclust(cust_scale, 
             kmeans, 
             method = "gap_stat", 
             nstart = 25,
             k.max = 10)+
  labs(title = "Gap Stat Diagram")

```
## Finding K Value Summary
Elbow Diagram: Gradient per increase-cluster began to level off after $K = 5$.
Silhouette Diagram: Max $S_{i_{max}}$ occurred at $K = 5$
Gap Stat Diagram: Shows the optimal K value is $K = 1$



# Visualise K-Mean Clustering Results
```{r}
 clusterings %>% 
  unnest(cols = c(augmented)) %>%
  filter(k <= 5) %>%
  ggplot(aes(x = score, y = income)) +
  geom_point(aes(color = .cluster))+
  labs(title = "Cluster Plot Diagram, K = 6")

```

## Result Summary
Diagram above showed the visualisation of the k-mean cluster plot for score vs. income with 5 groups of cluster. The variable we considers are `annual_income`, `spending_score` only. The diagram indicate a well-defined cluster group of 5, four groups are laying on on each corners and one in the middle. Albeit, there are evidence with overlapping data points between group 1 and group 2.

Overall, the data is suitable with k-mean clustering technique and yet it could be further improve the results by adding in the catagorical varaibles such as age group & gender to establish more insights towards the dataset.
