---
title: "Task01_Decathlon"
output: html_notebook
---

```{r}
library(tidyverse)
library(here)
```

```{r}
deca_raw <- read_rds("raw_data/decathlon.rds")
deca_raw
```

```{r}
# sanitize column names using janitor
deca_main <- janitor::clean_names(deca_raw)

# separate row name and reassign as column
athlete_name <- str_to_title(rownames(deca_main))
rownames(deca_main) <- NULL
deca_main <- cbind(athlete_name, deca_main)

# convert competition name into character variable
deca_main <- mutate(deca_main, competition = as.character(competition))

# reorder rank adjacent to competition name
deca_main <- deca_main[,c(1:11, 13, 12, 14)]

```

```{r}
# sanitize check for NA(s) for each column in the main dataframe
colSums(is.na(deca_main))
```


```{r}
names(deca_main)
as_tibble(deca_main)
```

## Analysis Question

## Question 1 - Longest long_jump seen
```{r}
deca_main %>% 
  select(athlete_name, long_jump) %>%
  slice_max(long_jump)
```
## Question 2 - Average 100m time in each competition
```{r}
deca_main %>% 
  select(x100m, competition) %>%
  group_by(competition) %>% 
  summarise_at(vars(x100m), list(avg_100m_time = mean))
```
## Question 3 - Who had the highest total points across both competitions?
```{r}
# gather points for Decastar.
deca_pts <- filter(deca_main, competition == "Decastar")
deca_pts <- select(deca_pts, athlete_name, points)
colnames(deca_pts)[2] <- "deca_points"

# gather points for olympicG
olym_pts <- filter(deca_main, competition == "OlympicG")
olym_pts <- select(olym_pts, athlete_name, points)
colnames(olym_pts)[2] <- "olym_points"

# joing both dataset together
total_pts <- inner_join(deca_pts, olym_pts)
total_pts <- mutate(total_pts, deca_points = as.numeric(deca_points))
total_pts <- mutate(total_pts, olym_points = as.numeric(olym_points))

# output the competitor with the highest point in both competitions.
total_pts %>%
      mutate(total_points = deca_points + olym_points) %>% 
    slice_max(total_points)
```
## Question 4 - What was the shot-put scores for the top three competitors in each competition?
```{r}
# select and slice to display the top 3 competitors for shot-put.
top_shot_put_scores <- select(deca_main, athlete_name, shot_put, competition) %>% 
  group_by(competition) %>% 
  slice_max(shot_put, n = 3)
top_shot_put_scores
```

## Question 5 - What was the average points for competitors:
## who ran the 400m in less than 50 seconds vs. 
## those who ran 400m in more than 50 seconds?

```{r}
# gather dataset for x400m, separate into groups of x400 >50 and <=50 seconds then average the output.
ran_400m <- select(deca_main, x400m, points) %>% 
  mutate(above_50sec = x400m > 50) %>% 
  group_by(above_50sec) %>%
  summarise_at(vars(points), list(avg_points = mean))
ran_400m
```

