---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(rtweet)
```

```{r}
cc_tweets <- read_csv("data/code_clan_tweets.csv")
cc_info <- read_csv("data/code_clan_info.csv")

names(cc_tweets)
names(cc_info)
```

```{r}
cc_tweets_noquote <- filter(cc_tweets, is_quote = TRUE)
cc_tweets_noquote %>% 
summarise (count = sum(na.rm = FALSE, favorite_count))

```

```{r}
cc_retweet_count <- cc_tweets_noquote %>% 
  group_by(source) %>% 
  summarise(mean_retweet = mean(retweet_count))
cc_retweet_count
```

Question 4.
- Assume that any tweets without a listed media type are of type “text”.
- Count the total number of likes (i.e. total of favorite_count), 
- split by media type, 
- arrange them from most likes to least. 

```{r}
cc_tweet_total_like <- cc_tweets %>% 
  mutate(media_type = coalesce(media_type, "text")) %>% 
  group_by(media_type) %>% 
  summarise(total_like = sum(na.rm = FALSE, favorite_count)) %>% 
arrange(desc(total_like))
cc_tweet_total_like
```

Question 5.
Find the mean number of characters that a CodeClan tweet contains.
You can either find a way to count the text in the text variable, 
or use the variable display_text_width which contains a count. 

Checking both would be a good idea if possible to see if they match (but it’s not essential).
```{r}
cc_tweets_textcount <- cc_tweets %>% 
summarise(mean_text_count = mean(na.rm = FALSE, display_text_width))
cc_tweets_textcount
```
Question 6.
- The code_clan_info.csv data file contains status_url along with other info.
- Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet.
- Decide which variable to join the tibbles on.

```{r}
cc_join_tweets <- cc_tweets %>% 
left_join(cc_join_tweets, cc_info,by ="tweet_id")

names(cc_join_tweets)
```

```{r}
code_hashtags <- cc_join_tweets

code_hashtags %>% 
select(tweet_id, hashtags.y) %>% 
mutate(hashtags.y = str_to_lower(hashtags.y))
```

