---
title: "Week05_Day_01_HW"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(CodeClanData)
library(janitor)

qb_rev <- clean_names(qb_revenue_breakdown)
qb_monsal <- clean_names(qb_monthly_sales)
qb_compe <- clean_names(qb_competitors)
qb_devdat <- clean_names(qb_device_data)
```

## Question 1 - Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.
```{r}
ggplot(qb_rev) +
       geom_col( aes(year, revenue,
            fill = revenue))
```

## Question 2 - Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year.

```{r}
mosales <- qb_monsal %>% 
  filter(cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot() +
  geom_line(aes(date, amount))
mosales

```

## Question 3　- Make a line chart showing monthly revenue and costs over the last year.

```{r}
rev_cash_sal <- qb_monsal %>% 
  filter(cashflow != "Kwikbit Unit 1 Sales") %>% 
  ggplot(aes(date, amount,  fill = amount)) +
  geom_line(aes(group = cashflow,colour = cashflow))+
    labs(
    title = "Monthly Revenue & Cost in 2019-2020",
    x = "Date",
    y = "Cost ($)"
  )
rev_cash_sal
```



## (Unfinish) Question 4　- Show annual sales of personal fitness trackers over the last 5 years broken down by company 

```{r}
# annual_sales_company <- qb_compe %>% 
#   group_by(company, year) %>% 
#   summarise(total_revenue = sum(revenue)) %>% 

#   ggplot(aes(year, total_revenue, fill = company, group = company)) +
#   geom_ribbon(stat='identity')
# 
# annual_sales_company
```
## Question 5　- Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines. 
```{r}
annual_sales_company <- qb_compe %>% 
  group_by(company, year) %>% 
  summarise(total_revenue = sum(revenue)) %>% 



  ggplot(aes(year, total_revenue ,  fill = total_revenue)) +
  geom_line(aes(group = company ,colour = company))+
    labs(
    title = "Annual Sales of Personal Fitness Trackers Per Company",
    subtitle = "2015 - 2019",
    x = "Year",
    y = "Revenue"
  )+
    scale_y_continuous(labels = scales::comma)
annual_sales_company
```

## Question 6　- Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people.
```{r}
  devdat <- qb_devdat %>% 
  select(c("device", "id", "counts")) %>% 
  group_by(device, id) %>% 
  summarise(total_count = sum(counts)) %>% 
  mutate(device = factor(device,levels = c("qikbit1", "competitor1", "competitor2", "competitor3")))

  devdat_plot <- ggplot(devdat, aes(id, total_count, fill = id))+
  geom_col(stat='identity')+
  facet_grid(~device)+
  scale_y_continuous(labels = scales::comma)+
   theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
devdat_plot
```









