---
title: "Week10 Day05 Homework 1"
output:
  html_document:
    df_print: paged
---

## Library
```{r}
library(tidyverse)
library(janitor)
library(lubridate)
library(modelr)
library(ggfortify)
library(GGally)
library(leaps)
library(glmulti)
library(caret)
```
## Load in Dataframe
```{r}
raw_avocado <- read_csv("1_weekend_homework_part1/data/avocado.csv")

## Sanity Check
# Find nas in data
raw_avocado %>% 
  summarise(across(.cols = everything(),.fns = ~sum(is.na(.))))
```


## Exploratory Analysis 
```{r}
main_avocado <- raw_avocado %>% 
  clean_names() %>% 
  select(-1) %>% 
  rename(small = "x4046",
         medium = "x4225",
         large = "x4770",
         is_organic = type) %>% 
  mutate(is_organic = as.logical(if_else(is_organic == "organic", 1, 0)),
         year = as.factor(year),
         region = as.factor(region),
         month = month(ymd(date)),
         season = case_when(
           month == c(12,1,2) ~ "4",
           month == c(3,4,5) ~ "1",
           month == c(6,7,8) ~ "2",
           TRUE ~ "3"),
         season = factor(season))
```

## Diagnostics Plot
```{r}
avocado <- main_avocado %>% 
  select(-date, -region, -month, - year, -total_bags)

num_avocado <- avocado %>% 
  select_if(is.numeric)

nnum_avocado <- avocado %>% 
  select_if(function(x) !is.numeric(x))

nnum_avocado$average_price <- num_avocado$average_price 

# Convert numeric df into log scale since the distrubution are all askews and non-correlated
# Mutate All inf & -inf into 0 
lognum_avocado = log(num_avocado)%>% 
  mutate_all(function(x) ifelse(is.infinite(x), 0, x)) 

# Construct df with log numbers combine with non-numeric variables.
# Remove total_bags to avoid multicollinearity
log_avocado <- bind_cols(lognum_avocado, nnum_avocado[1:ncol(nnum_avocado)-1])

ggpairs(num_avocado)
ggpairs(lognum_avocado)
ggpairs(nnum_avocado)
```

# Manual Modelling

- Choose Season as the first predictor
- All P values are falling below 5%alpha
- Good diagnostic plots showing homoscedasticity for RvF & SL plots along with good fits for the NQ-Q

### Model A - total_volume vs average_price
```{r}
moda <- lm(average_price ~ total_volume, data = log_avocado)
summary(moda)
autoplot(moda)
```
### Model B - is_organic
```{r}
modb <- lm(average_price ~ total_volume + is_organic, data = log_avocado)
summary(modb)
anova(moda,modb)
```


### Model B - Find Next Perdictor
```{r}

avocado_modb_resid <- log_avocado %>%
  add_residuals(moda) %>%
  select(-c("average_price", "total_volume", "is_organic"))

avocado_modb_resid %>% 
  ggpairs()
```

### Model C - season
```{r}
# Checked with avg_price vs season diagnostic plot, everything is good.
modc <- lm(average_price ~ total_volume + is_organic + season, data = log_avocado)
summary(modc)
anova(modc, modb)
```

### Model C - Find Next Perdictor
```{r}

avocado_modc_resid <- log_avocado %>%
  add_residuals(modb) %>%
  select(-c("average_price", "total_volume", "is_organic", "season"))

avocado_modc_resid %>% 
  ggpairs()
```

### Model D - large_bags
```{r}
# Checked with avg_price vs season diagnostic plot, everything is good.
modd <- lm(average_price ~ total_volume + is_organic + season + large_bags, data = log_avocado)
# autoplot(modd)
summary(modd)
anova(modc, modd)
```


### Model D - Find Next Perdictor
```{r}

avocado_modd_resid <- log_avocado %>%
  add_residuals(modc) %>%
  select(-c("average_price", "total_volume", "is_organic", "season", "large_bags"))

avocado_modd_resid %>% 
  ggpairs()
```

### Model E - Medium
```{r}
# Checked with avg_price vs season diagnostic plot, everything is good.
manual_model <- lm(average_price ~ total_volume + is_organic + season + large_bags + medium, data = log_avocado)
summary(manual_model)
anova(modd, manual_model)
autoplot(manual_model)
```

# Model_E relative importance analysis.
- season       0.01748384
- total_volume 0.29870614
- is_organic   0.35751411
- large_bags   0.16599661
- medium       0.16029929
```{r}
relaimpo::calc.relimp(manual_model, type = "lmg", rela = TRUE)

a <- broom::glance(modc)%>% 
  select(1,2,8,9)
b <- broom::glance(modd)%>% 
  select(1,2,8,9)
c <- broom::glance(manual_model) %>% 
  select(1,2,8,9)

manual_modelling_result <- bind_rows(a,b,c) %>% 
  add_column(model_name = c("c", "d", "final"), .before = "r.squared")
manual_modelling_result
```



# Automatic Modelling - Full Mode Exhaustive Method

### Best 5 Predictors 
- is_organic(11)
- total_volume(9)
- medium(9)
- small_bags(8)
- large_bags(8)

```{r}
regsubset_exhaustive <- regsubsets(average_price~.,
                                   data = log_avocado,
                                   nvmax = 11,
                                   method = "exhaustive")


sum_regsubset_exhaustive <- summary(regsubset_exhaustive)
sum_regsubset_exhaustive
```




# Exhaustive Method Summary
- total_volume, medium, small_bags, large_bags, x_large_bags, is_organic, season
```{r}
# Penalized measure with adjusted R Squared
plot(regsubset_exhaustive, scale = "adjr2")
# Penalized measure with bic


plot(sum_regsubset_exhaustive$bic, type = "b")
# R-squared value
plot(sum_regsubset_exhaustive$rsq, type = "b")

# Show 7-predictors model: 
# summary(regsubset_exhaustive)$which[7,]
# total_volume, medium, total_bags, small_bags, large_bags, x_large_bags, is_organic,season4 (winter)
```

### Anova with season
Results shows P value of ~0 meaning season predictor is infact stat-significant 
Diagnostic plots shows good relations between residuals plots,
Ideal for Normal Q-Q plot with slight, askew on the left
```{r}
# model without seasons
exhaustive_model_nosea <- lm(average_price ~ total_volume + medium + small_bags + large_bags + x_large_bags + is_organic, data = log_avocado)

# model with seasons
exhaustive_model <- lm(average_price ~ total_volume + medium + small_bags + large_bags + x_large_bags + is_organic + season, data = log_avocado)

summary(exhaustive_model)
anova(exhaustive_model_nosea, exhaustive_model)


autoplot(exhaustive_model)
```

# GLMulti - Genetic Algorithm for the 7-models predictors
Note: Takes a long time to run
```{r}
# glmuti_avocado <- log_avocado %>%
#   select(average_price, total_volume, medium, small_bags, large_bags, x_large_bags, is_organic, season)
# 
# glmulti_fit <- glmulti(
#   average_price ~ .,
#   data = glmuti_avocado,
#   level = 2, # 2 = include pairwise interactions, 1 = main effects only (main effect = no pairwise interactions)
#   minsize = 0, # no min size of model
#   maxsize = -1, # -1 = no max size of model
#   marginality = TRUE, # marginality here means the same as 'strongly hierarchical' interactions, i.e. include pairwise interactions only if both predictors present in the model as main effects.
#   method = "g", # the problem is too large for exhaustive search, so search using a genetic algorithm
#   crit = bic, # criteria for model selection is BIC value (lower is better)
#   plotty = FALSE, # don't plot models as function runs
#   report = FALSE, # do produce reports as function runs
#   confsetsize = 50, # return best 100 solutions
#   fitfunction = lm # fit using the `lm` function
# )
# 
# summary(glmulti_fit)
```

# GA Results
- season:x_large_bags' p-value is above 0.05, hence there is insignificant difference when adding season:x_large_bags terms
```{r}
genetic_moda <-    lm(average_price ~ total_volume + season + medium + small_bags +              
                        large_bags + x_large_bags + is_organic + medium:total_volume +            
                        small_bags:total_volume + large_bags:total_volume + large_bags:medium +    
                        large_bags:small_bags + x_large_bags:medium + x_large_bags:small_bags +  
                        x_large_bags:large_bags + is_organic:total_volume + is_organic:small_bags + 
                        is_organic:large_bags + is_organic:x_large_bags + season:x_large_bags, data = log_avocado)

summary(genetic_moda)
# autoplot(genetic_moda)
```

```{r}
genetic_model <-    lm(average_price ~ total_volume + season + medium + small_bags +              
                        large_bags + x_large_bags + is_organic + medium:total_volume +            
                        small_bags:total_volume + large_bags:total_volume + large_bags:medium +    
                        large_bags:small_bags + x_large_bags:medium + x_large_bags:small_bags +  
                        x_large_bags:large_bags + is_organic:total_volume + is_organic:small_bags + 
                        is_organic:large_bags + is_organic:x_large_bags, data = log_avocado)

summary(genetic_model)
# autoplot(genetic_model)
```



# K-Fold-Validation 
## Manual
manual_model <- lm(average_price ~ total_volume + is_organic + season + large_bags + medium, data = log_avocado)
```{r}

fold20_model <- trainControl(method = "cv", # cross-validation
                           number = 20, # 20-fold
                           savePredictions = TRUE) # save all predictions

kfold_manual_model <- train(average_price ~ total_volume + is_organic + season + large_bags + medium, 
               data = log_avocado,
               trControl = fold20_model, # use options defined above
               method = 'lm')

kfold_exhaustive_model <- train(average_price ~ total_volume + medium + small_bags + large_bags + x_large_bags + is_organic + season, 
               data = log_avocado,
               trControl = fold20_model, # use options defined above
               method = 'lm')

kfold_genetic_model <- train(average_price ~ total_volume + season + medium + small_bags +              
                        large_bags + x_large_bags + is_organic + medium:total_volume +            
                        small_bags:total_volume + large_bags:total_volume + large_bags:medium +    
                        large_bags:small_bags + x_large_bags:medium + x_large_bags:small_bags +  
                        x_large_bags:large_bags + is_organic:total_volume + is_organic:small_bags + 
                        is_organic:large_bags + is_organic:x_large_bags, 
               data = log_avocado,
               trControl = fold20_model, # use options defined above
               method = 'lm')
```

# Results
```{r}
# Validation Results
type <-  c("manual", "exhaustive", "genetic")
rmse <- c(mean(kfold_manual_model$resample$RMSE), mean(kfold_exhaustive_model$resample$RMSE),mean(kfold_genetic_model$resample$RMSE) )
rsq <- c(mean(kfold_manual_model$resample$Rsquared), mean(kfold_exhaustive_model$resample$Rsquared),  mean(kfold_genetic_model$resample$Rsquared))

result_validation <- data.frame(type, rmse, rsq)

# Model Selection Results
# summary(manual_model)
# summary(exhaustive_model)
# summary(genetic_model)

a <- broom::glance(manual_model)%>% 
  select(1,2,8,9)
b <- broom::glance(exhaustive_model)%>% 
  select(1,2,8,9)
d <- broom::glance(genetic_model)%>% 
  select(1,2,8,9)

result_model <- bind_rows(a,b,d) %>% 
  add_column(model_name = c("Manual", "Exhaustive", "Genetic"), .before = "r.squared")

# Final Model Selection Results
result_final <- bind_cols(result_model, result_validation) %>% 
  select(-type)
result_final
```


