---
title: "week05_day02_hw"
output: html_notebook
---


```{r}
library(tidyverse)
```
# Question 1 - Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}
raw_backpack <- CodeClanData::backpack
main_backpack <- janitor::clean_names(raw_backpack)
colnames(main_backpack)
```


# Question 2 - What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.
```{r}
ques_02 <- ggplot(main_backpack, aes(x = backpack_weight)) +
                geom_histogram(binwidth = (1),color = "black", fill = "gray")+
                labs(
                x = "Backpack Weight (kg)",
                y = "Count",
                title = "Backpack Weight Distribution"
              )
ques_02
```


# Question 3 - Are there differences in backpack weight between sex?
# Answer 3 - No
```{r}
ques_03 <- 
  ggplot(main_backpack, aes(x = backpack_weight)) +
                geom_histogram(main_backpack = subset(main_backpack, sex = "Male"), binwidth = (1), fill = "green", alpha = 0.2)+
                geom_histogram(main_backpack = subset(main_backpack, sex = "Female"), binwidth = (1), colour = "black", fill = "purple", alpha = 0.2)+
                labs(
                x = "Backpack Weight (kg)",
                y = "Count",
                title = "Backpack Weight Distribution"
              )
ques_03
```

# Question 4 - What is the relationship between body weight and backpack weight?
# Answer 4 - No relationship
```{r}
ques_04 <- ggplot(main_backpack,
       aes(x = body_weight, y = backpack_weight))+
    geom_point()+
  geom_smooth()+
  labs(
    x = "\n Body Weight",
    y = "Backpack Weight",
    title = "Question 4 - Relationship between body weight and backpack weight",
  )

ques_04
```

# Question 5 - Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.
# Answer 5 - Female's reltionship are more concentrate than male.
```{r}
ques_05 <- ggplot(main_backpack,
       aes(x = body_weight, y = backpack_weight))+
    geom_point()+
  geom_smooth()+
  facet_grid(~sex,)+
  labs(
    x = "\n Body Weight",
    y = "Backpack Weight",
    title = "Question 5 - Relationship between body weight and backpack weight",
  )

ques_05
```
# Question 6 - What proportion of students report back pain?
```{r}

ques_06 <- main_backpack %>% 
  group_by(back_problems) %>% 
  summarise(back_pain = table(back_problems)) %>% 
  mutate( back_problems = case_when(
    back_problems == 1 ~ "Yes",
    back_problems == 0 ~ "No",
    TRUE ~ "No"
  )) %>% 
  as.data.frame()

ques_06 <- ggplot(ques_06,
           aes(x=back_problems, y= back_pain)) +
    geom_bar(stat="identity")+
    # facet_grid(~prognosis,)+
  labs(
    x = "Back Pain",
    y = "Count",
    title = "Back Problem",
  )
ques_06
```



# Question 7 - Is this proportion different between men and women?
```{r}
ques_07 <- main_backpack %>% 
  group_by(sex, back_problems) %>% 
  summarise(back_pain = table(back_problems)) %>% 
  mutate( back_problems = case_when(
    back_problems == 1 ~ "Yes",
    back_problems == 0 ~ "No",
    TRUE ~ "No"
  )) %>% 
  as.data.frame()


ques_07 <- ggplot(ques_07,
           aes(x=back_problems, y= back_pain, fill = back_problems)) +
    geom_col()+
      facet_grid(~sex,)+
  labs(
    x = "Back Pain ( Per gender)",
    y = "Count",
    title = "Back Problem"
  )+
    scale_fill_manual(values = c('green', 'red'),
                               guide = "none")

ques_07

```

# Question 8 - Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.






