---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
```


```{r}

weather_forecast <- list(
"Thu" = list(temp = 7, rain_chance = "52%", wind_speed = "8KMPH"),
"Fri" = list(temp = 5,  rain_chance = "6%", wind_speed = "10KMPH"),
"Sat" = list(temp = 8, rain_chance = "27%", wind_speed = "8KMPH")
)
```


5°C	4°C	4°C	5°C	4°C	4°C	4°C	4°C

```{r}
fortnight_Temp <- list(6, 6, 9, 11, 8, 10, 11, 12, 10, 9, 9, 8, 8, 7)
fortnight_forecast <- matrix(fortnight_Temp, 2:7, byrow= TRUE)
fortnight_forecast

class (fortnight_forecast)
#Q2i
fortnight_forecast[2,3]
#Q2ii
fortnight_forecast[2,]
#Q2iii
fortnight_forecast[1:2, c(1,3,5)]
```

Question 5.
Write a function that pre-appends “The answer is:” to any character input, 

while for numeric input,returns the number for numbers less than 10,
or divides the number by 10 for numbers greater than 10. 
For anything else return “Invalid input”.


If x<10, display x
If x>=10, x= x/10, display x

Else, "Invalid input
Output paste0"The answer is: ", x, "."
```{r}
output_quote = "The answer is: "

num_checker <- function(x) {
  if (is.numeric(x)) {
    ifelse(x < 10, {
      paste0(output_quote, x, "!")
    }, {
      x <- x / 10
      {
        paste0(output_quote, x, "!")
      }
    })
  }
  else{
    paste0("Invalid Input!")
  }
}

  

num_checker(9)
num_checker(10)
num_checker("ABC")
num_checker("ASD!£*(&!£&*")

```




```{r}
x1 <- c(1, 5, 3, - 3, 5, - 7, 8)    
y1 <- c(6, 6, 9, 11, 8, 10, 11, 12, 10, 9, 9, 8, 8, 7)

check_numrow <- function(x){length(x)}


check_array <- function(x,y){ If(check_numrow(x) = check_numrow(y)){
  ifelse(all(x,y)= TRUE,{
    outputx = 2}, {
      num_list = 1:check_numrow(x);
      outputx = 1;
      while(outputx = 1){
        for(n in num_list){
          if (x[n] != y[n]){outputx = 2}
        }}}
      }
           }else{ outputx = 3}
  
  
 
  case_when(
    outputx ==1 ~ return("Exactly the same")
    outputx ==2 ~ return("The same")
    outputx ==3 ~ return("Different")
            ) 
}



  
  num_list = 1:check_numrow(x)
  For (n in num_list){
    if(x[n] == y[n],n<-n+1)
    










}

```
set numrow

If num(x1) = num(x2),
Then

For 1: numrow 
if the (n) element = (n) element x2, outputx = 1
loop until n = numrow
elseif
if all(x1,x2) = TRUE, outputx = 2
If num(x1) != num(x2), Then outputx = 3